SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-03 scipy-1.0/paper.tex
Brought back numba by request

As of SciPy version 0.19, it is possible for users to wrap low-level functions
in a \texttt{scipy.LowLevelCallable} object that reduces the overhead of
calling compiled C functions directly from Python.  
Supported low-level functions include \texttt{PyCapsule} 
objects, \texttt{ctypes} function pointers, and \texttt{cffi} function pointers. 
Furthermore, it is even possible to generate a low-level callback function 
automatically from a Cython module using \texttt{scipy.LowLevelCallable.from\_cython}.

>>>>

As of SciPy version 0.19, it is possible for users to wrap low-level functions
in a \texttt{scipy.LowLevelCallable} object that reduces the overhead of
calling compiled C functions, such as those generated using \texttt{numba}
or Cython, directly from Python.  
Supported low-level functions include \texttt{PyCapsule} 
objects, \texttt{ctypes} function pointers, and \texttt{cffi} function pointers. 
Furthermore, it is even possible to generate a low-level callback function 
automatically from a Cython module using \texttt{scipy.LowLevelCallable.from\_cython}.
